RDF Validation Requirements - Evaluation and Logical Underpinning

### 2015-01-17 paper/RDF validation requirements/RDF validation requirements.tex
CWA/UNA dependency evaluation

@@

>>>>

\newenvironment{evaluation-cwa-una-dependency}{
  \scriptsize
  \sffamily
  \vspace{0cm}
	\begin{center}
  \begin{tabular}{l|c}
  \hline
  \textbf{Constraint Type} & \textbf{CWA/UNA Dependent} \\
  \hline

@@

\subsection{Evaluation of CWA/UNA Dependency}

\begin{evaluation-cwa-una-dependency}
*Subsumption & $\checkmark$ \\
*Class Equivalence & \ding{55} \\
*Sub Properties & $\checkmark$ \\
*Property Domain & $\checkmark$ \\ 
*Property Range & $\checkmark$ \\ 
*Inverse Object Properties & $\checkmark$ \\ 
*Symmetric Object Properties & $\checkmark$ \\ 
*Asymmetric Object Properties & $\checkmark$ \\ 
*Reflexive Object Properties & $\checkmark$ \\ 
*Irreflexive Object Properties & $\checkmark$ \\
Disjoint Properties & \ding{55} \\ 
Disjoint Classes & \ding{55} \\
Context-Sp. Property Groups & \ding{55} \\ 
Context-Sp. Inclusive OR of P. & \ding{55} \\
Context-Sp. Inclusive OR of P. Groups & \ding{55} \\ 
Recursive Queries & \ding{55} \\ 
Individual Inequality & $\checkmark$ \\ 
*Equivalent Properties & \ding{55} \\ 
Property Assertions & \ding{55} \\ 
Data Property Facets & \ding{55} \\ 
Literal Pattern Matching & \ding{55} \\ 
Negative Literal Pattern Matching & \ding{55} \\ 
*Object Property Paths & $\checkmark$ \\ 
*Intersection & $\checkmark$ \\ 
*Disjunction & $\checkmark$ \\ 
*Negation & $\checkmark$ \\ 
*Existential Quantification & $\checkmark$ \\ 
*Universal Quantification & $\checkmark$ \\ 
*Minimum Unqualified Cardinality & $\checkmark$ \\ 
*Minimum Qualified Cardinality & $\checkmark$ \\ 
*Maximum Unqualified Cardinality & $\checkmark$ \\ 
*Maximum Qualified Cardinality & $\checkmark$ \\ 
*Exact Unqualified Cardinality & $\checkmark$ \\ 
*Exact Qualified Cardinality & $\checkmark$ \\ 
*Transitive Object Properties & $\checkmark$ \\ 
Context-Sp. Exclusive OR of P. & $\checkmark$ \\ 
Context-Sp. Exclusive OR of P. Groups & $\checkmark$ \\
Allowed Values & $\checkmark$ \\ 
Not Allowed Values & $\checkmark$ \\ 
Literal Ranges & \ding{55} \\ 
Negative Literal Ranges & \ding{55} \\ 
Required Properties & $\checkmark$ \\ 
Optional Properties & \ding{55} \\
Repeatable Properties & $\checkmark$ \\ 
Negative Property Constraints & $\checkmark$ \\ 
*Individual Equality & $\checkmark$ \\ 
*Functional Properties & $\checkmark$ \\
*Inverse-Functional Properties & $\checkmark$ \\ 
*Value Restrictions & $\checkmark$ \\
*Self Restrictions & $\checkmark$ \\
Primary Key Properties & $\checkmark$ \\ 
*Class-Specific Property Range & $\checkmark$ \\ 
*Class-Sp. Reflexive Object P. & $\checkmark$ \\ 
Membership in Controlled Vocabularies & $\checkmark$ \\ 
IRI Pattern Matching & \ding{55} \\ 
Literal Value Comparison & \ding{55} \\ 
Define Order & \ding{55} \\ 
Validation Levels & \ding{55} \\ 
String Operations & \ding{55} \\ 
\end{evaluation-cwa-una-dependency}

\begin{evaluation-cwa-una-dependency}
Context-Specific Valid Classes & \ding{55} \\
Context-Specific Valid Properties & \ding{55} \\ 
Default Values & \ding{55} \\ 
Mathematical Operations & \ding{55} \\ 
Language Tag Matching & \ding{55} \\ 
Language Tag Cardinality & $\checkmark$ \\ 
Whitespace Handling & \ding{55} \\ 
HTML Handling & \ding{55} \\ 
Conditional Properties & $\checkmark$ \\ 
Recommended Properties & \ding{55} \\ 
Handle RDF Collections & \ding{55} \\ 
Value is Valid for Datatype & \ding{55} \\ 
*Exploiting Class/Property Specialization Ontology Axioms & \ding{55} \\ 
*Cardinality Shortcuts & $\checkmark$ \\ 
Aggregations & \ding{55} \\ 
\end{evaluation-cwa-una-dependency}

% -----
